% LaTeX mini project proposal (minimal template)
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\title{Mini Project Proposal: Stock Price Prediction}
\author{Sivanandarajah V., Srivaxshana M., Suwaathmi R., Thurga R.}
\date{07/02/2026}
\begin{document}
\maketitle
\tableofcontents
\section{Problem Statement}
Stock price prediction is a complex and challenging task due to the highly volatile, nonlinear, and time-dependent nature of financial markets. Traditional statistical models and basic machine learning approaches often fail to capture long-term temporal dependencies present in historical stock price data, leading to inaccurate forecasts and unreliable investment decisions. This project will use LSTM networks to model long-range dependencies and improve prediction accuracy.
\section{Objectives}
\begin{itemize}
  \item Analyze historical stock market data using AI techniques.
  \item Design and implement an LSTM-based stock price prediction model.
  \item Preprocess and normalize time-series data and evaluate model performance.
\end{itemize}
\section{Methodology}
Data will be collected from the S\&P 500 dataset, cleaned, normalized, and transformed to supervised learning format using sliding windows. An LSTM-based neural network will be trained and evaluated using MSE and RMSE. Results and visual comparisons will be included.
\section{Dataset}
The dataset is the S\&P 500 5-year dataset (CSV) from Kaggle; it contains daily OHLC and volume and ticker symbols.
\section{Expected Outcomes}
Trained LSTM model, performance evaluation, visualizations, source code, and final report.
\section{AI Involvement}
The project focuses on LSTM-based learning, preprocessing, model training, and evaluation; AI involvement is above 85\%.
\end{document}
